### 2014-04-16 doc/uist14/iteration3.tex
problem statement

%!TEX root = uist14.tex
\section{Iteration 3: Head motion refinement}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the
near-eye display for the refinement step. This has two problems: First, a
spatial layout of targets is compressed into a uni-dimensional list. List
navigation commands thus have poor spatial mapping. Second, our techniques
require the user to switch their focus back and forth between the physical
world and the display. These issues motivated us to design an approach that
also utilizes orientation information during the {\em refinement} stage, to
provide a more direct mapping between the user's actions and target selection.

\achal{This used to have an explicit question which I removed, as it sounded
very unnatural.}
In our third iteration, we build a system which further minimizes the chance of
falling back to list based refinement.

>>>>

%!TEX root = uist14.tex
\section{Iteration 3: Head motion refinement}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the
near-eye display for the refinement step. The list interface has a few clear shortcomings: navigation actions map poorly to real world results, and the users must switch their focus back and forth between the physical scene and the near-eye display. These problems motivated us to design an approach that harnesses the head orientation during the {\em refinement} stage.

In our third iteration, we build a system which further minimizes the chance of
falling back to list based {\em refinement}.
